Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-11 text/supp.tex
Switch back bib style and bump version
Tweak text to work with thesis
Remove a causes table column and reduce width

\LTcapwidth=\textwidth
\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{3.2cm}>{\RaggedRight}p{6.5cm}>{\RaggedRight}p{5.0cm}}
%\caption{Phylopic credits}\\
\toprule
\input{../analysis/phylopic.tex}
\label{tab:phylopic}
\end{longtable}
\end{footnotesize}
\onehalfspacing

\bibliographystyle{ecologyletters}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}

@@

\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{1.5cm}>{\RaggedRight}p{4.3cm}>{\RaggedRight}p{0.8cm}>{\RaggedRight}p{1.7cm}>{\RaggedRight}p{1.0cm}>{\RaggedRight}p{3.0cm}>{\RaggedRight}p{1.7cm}>{\RaggedRight}p{1.3cm}}

\caption[All populations with Pr$(\nu < 10) > 0.5$ in the base heavy-tailed
  Gompertz population dynamics model.]{All populations with Pr$(\nu < 10) > 0.5$ in the base heavy-tailed
  Gompertz population dynamics model. Shown are the log abundance time series,
  population descriptions, Global Population Dynamics Database Main IDs,
  citation for the data source or separate verification literature, a
  description of the cause of the black swan events (if known), the
  probability of heavy tails as calculated by our model, and median estimate
  of $\nu$ from our model with 90\% quantile credible intervals indicated in
  parentheses. Red dots on the time series indicate downward black-swan events
  and blue values indicate upward black-swan events that have a $10 \cdot
  10^{-4}$ probability or less of occurring if the population dynamics were
  explained by a Gompertz model with normally distributed process noise with a
  standard deviation equal to the scale parameter in the fitted t
  distribution.}\\

\toprule
\input{../analysis/cause-table.tex}
\label{tab:causes-supp}
\end{longtable}
\end{footnotesize}
\onehalfspacing

@@

\begin{spacing}{1.15}
\begin{footnotesize}
\begin{verbatim}
data {
  int<lower=3> N;              // number of observations
  vector[N] y;                 // vector to hold ln abundance observations
  real<lower=0> nu_rate;       // rate parameter for nu exponential prior
}
parameters {
  real lambda;                 // Gompertz growth rate parameter
  real<lower=-1, upper=2> b;   // Gompertz density dependence parameter
  real<lower=0> sigma_proc;    // process noise scale parameter
  real<lower=2> nu;            // t-distribution degrees of freedom
  real<lower=-1, upper=1> phi; // AR1 parameter
  vector[N] U;                 // unobserved states
  real<lower=0> sigma_obs;     // specified observation error SD
}
transformed parameters {
  vector[N] epsilon;           // error terms
  epsilon[1] <- 0;
  for (i in 2:N) {
    epsilon[i] <- U[i] - (lambda + b * U[i - 1])
                       - (phi * epsilon[i - 1]);
  }
}
model {
  // priors:
  nu ~ exponential(nu_rate);
  lambda ~ normal(0, 10);
  sigma_proc ~ cauchy(0, 2.5);
  phi ~ normal(0, 1);
  // data model:
  for (i in 2:N) {
    U[i] ~ student_t(nu,
                     lambda + b * U[i - 1]
                     + phi * epsilon[i - 1],
                     sigma_proc);
  }
  y ~ normal(U, sigma_obs);
}
\end{verbatim}
\end{footnotesize}

@@

\begin{footnotesize}
\noindent
{\tt
\input{../analysis/mainids}
}
\end{footnotesize}
\end{spacing}

>>>>

\LTcapwidth=\textwidth
%\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{3.2cm}>{\RaggedRight}p{6.5cm}>{\RaggedRight}p{5.0cm}}
%\caption{Phylopic credits}\\
\toprule
\input{../analysis/phylopic.tex}
\label{tab:phylopic}
\end{longtable}
\end{footnotesize}
%\onehalfspacing

\renewcommand{\baselinestretch}{\tighttextstretch}
\normalsize
\bibliographystyle{apalike}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}
\renewcommand{\baselinestretch}{\textstretch}
\normalsize

@@

%\singlespacing
\begin{footnotesize}
\begin{longtable}{>{\RaggedRight}m{1.4cm}>{\RaggedRight}p{3.3cm}>{\RaggedRight}p{0.7cm}>{\RaggedRight}p{1.5cm}>{\RaggedRight}p{3.0cm}>{\RaggedRight}p{1.4cm}>{\RaggedRight}p{1.25cm}}

\caption[All populations with Pr$(\nu < 10) > 0.5$ in the base heavy-tailed
  Gompertz population dynamics model.]{All populations with Pr$(\nu < 10) > 0.5$ in the base heavy-tailed
  Gompertz population dynamics model. Shown are the log abundance time series,
  population descriptions, Global Population Dynamics Database Main IDs,
  citation for the data source or separate verification literature, a
  description of the cause of the black swan events (if known), the
  probability of heavy tails as calculated by our model, and median estimate
  of $\nu$ from our model with 90\% quantile credible intervals indicated in
  parentheses. Red dots on the time series indicate downward black-swan events
  and blue values indicate upward black-swan events that have a $10^{-4}$ probability or less of occurring if the population dynamics were
  explained by a Gompertz model with normally distributed process noise with a
  standard deviation equal to the scale parameter in the fitted t
  distribution.}\\

\toprule
\input{../analysis/cause-table.tex}
\label{tab:causes-supp}
\end{longtable}
\end{footnotesize}
%\onehalfspacing

@@

%\begin{spacing}{1.15}
\begin{footnotesize}
\begin{verbatim}
data {
  int<lower=3> N;              // number of observations
  vector[N] y;                 // vector to hold ln abundance observations
  real<lower=0> nu_rate;       // rate parameter for nu exponential prior
}
parameters {
  real lambda;                 // Gompertz growth rate parameter
  real<lower=-1, upper=2> b;   // Gompertz density dependence parameter
  real<lower=0> sigma_proc;    // process noise scale parameter
  real<lower=2> nu;            // t-distribution degrees of freedom
  real<lower=-1, upper=1> phi; // AR1 parameter
  vector[N] U;                 // unobserved states
  real<lower=0> sigma_obs;     // specified observation error SD
}
transformed parameters {
  vector[N] epsilon;           // error terms
  epsilon[1] <- 0;
  for (i in 2:N) {
    epsilon[i] <- U[i] - (lambda + b * U[i - 1])
                       - (phi * epsilon[i - 1]);
  }
}
model {
  // priors:
  nu ~ exponential(nu_rate);
  lambda ~ normal(0, 10);
  sigma_proc ~ cauchy(0, 2.5);
  phi ~ normal(0, 1);
  // data model:
  for (i in 2:N) {
    U[i] ~ student_t(nu,
                     lambda + b * U[i - 1]
                     + phi * epsilon[i - 1],
                     sigma_proc);
  }
  y ~ normal(U, sigma_obs);
}
\end{verbatim}
\end{footnotesize}

@@

\renewcommand{\baselinestretch}{\tighttextstretch}
\normalsize
\begin{footnotesize}
\noindent
{\tt
\input{../analysis/mainids}
}
\end{footnotesize}
\renewcommand{\baselinestretch}{\textstretch}
\normalsize
%\end{spacing}
